Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-25 papers/B1555_EdgeOn/B1555_letter.tex
text change in Modelling and Discussion

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In $K^\prime$ band
imaging (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. The from the edge-on disk can explain why there is no detection of image B \& D in near-infrared (Fig 1, right). Its orientation is aligned with image B \& D. With this new information from AO image, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 2. Both
of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux ratios. The comparison of observation and our lens modelling is
in Figure 3, Table 3 \& 4.

@@

\section{Discussion}
The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies. Discrepency between numerical simulation and observation within the local universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe. Difficulties emerge while searching beyond the Local Group due to the low luminosity of satellites. This makes gravitational lensing a powerful tool for the detection of substructures. With the fact that surface brightness is sensitive to gravitational perturbation, flux ratio anomaly in strong lensing system becomes a sign of existence of subhalo and also reflects its total mass. Give directly measurement of mass function which can avoid making assumptions on how baryonic matter distributes with dark matter.

Discussions on substructure searching in strong lensing system are mostly done by multiple images of lensed quasar. In the ideal case (no extinction and micro lensing), flux ratio anomalies are brought by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential. Numerical simulations have examined this idea with known lensed quasars. In \citet{Xu14}, they found that substructure cannot expalin for all of radio flux anomalous phenomena. Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system. The rest of them are only few percent likely to have substructure origined flux anomaly, including our target B1555+375. They conclude B1555+375 with improper lens model. This result can be supported by SHARP $K^{\prime}$ band image, which an edge-on disk lies across between the radio merging double A \& B. A more complex lens model (e.g. include an exponential disk) must be applied on B1555+375.

In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models predict the radio image positions and flux ratio anomaly between components A and B, which the 1-SIE model in \citet{Marlow} fails. Since radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}, our successful modelling indicates that the structure from lens galaxy itself can cause radio flux ratio anomalies. An edge-on disk with high ellipcity can well explain the observed flux ratios and substructure is not neccessary to presence. Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars. A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar. Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future. One must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis. For the case oringinated by real  substructures, mass distribution of lens galaxy may also influence the estimated mass and other derived properties. We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar. For precise estimation on substurcture population, mass function, or any derived properties from strong lensed flux anomalous quasars, non-substructure effects are important to be understood beforehand.

Our result also shows that multi-wavelength image is helpful on exploring flux anomalous lensed quasars. Although radio band provides reliable data on position and fluxe of lensed images, optical and near-infrared imaging provides useful information about mass distribution of lens galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling. The improvement is even more dramatic in B1555+375 while adding an edge-on disk can well explain flux ratio anomaly. Lack of knowledge on lens galaxy surely leads to an improper lens model sometimes and can have impacts on statics and derived properties among substructure detection. With the first system being analyzed and shown that an edge-on disk can explain its flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\

>>>>

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In $K^\prime$ band
imaging (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $\approx 10$ degree. The detection of edge-on disk also explain the missing images B \& D in near-infrared (Fig 1, right). Image B \& D very likely are extincted by the edge-on disk since the images have the same orientation with the disk.

By adding a disk component, we apply our new discover from AO image to the
B1555+375 modelling. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+expdisk). And the second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 2. Both
of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux ratios. The comparison of observation and our lens modelling is
in Figure 3, Table 3 \& 4.

@@

\section{Discussion}
The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies. Discrepency between numerical simulation and observation within the local universe gives two possible interpretations: an alternative structure formation model or small sample arise from nowaday observation. Difficulties emerge in direct detection when searching beyond the Local Group. Until now, most of known satellites are at high mass end in the mass function. However, the gravitational perturbations from substructures can cause detectable change in surface brightness among lensed images. This makes gravitational lensing a powerful tool for searching substructures. Flux ratio anomalies in strongly lensed quasars become a sign of existence of subhalo. Total mass of substructures can be derived from their gravitational effects and also give direct measurement of mass function which avoid making assumptions on baryonic matter distribution assoociated with dark matter.

In the most of discussions upon multiple image lensed quasars, flux ratio anomalies are brought only by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential (in ideal case, i.e. no dust extinction, micro lensing, scattering etc.). Numerical simulations have examined this idea with known flux anomalous lensed quasars. In \citet{Xu14}, they found that substructure cannot expalin for all of these radio flux anomalies. Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system. The rest of them are only few percent likely to have substructure originated flux anomaly, including our target B1555+375. They conclude the failure on B1555+375 with improper lens model. Their result can be supported by SHARP $K^{\prime}$ band image, which an edge-on disk lies across between the radio merging double A \& B. A more complex lens model (e.g. include an exponential disk) must be considered for B1555+375.

In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk components. Our models predict the radio image positions and also flux ratio anomalies, which the 1-SIE model in \citet{Marlow} fails. Since radio propagation effects are ruled out in B1555+375 \citep{K03,KD04}, our successful modelling indicates that the structure from lens galaxy itself can cause radio flux ratio anomalies. An edge-on disk with high ellipcity in lens models well explains the observed flux ratios without the presense of substructrues. Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasars indicate the existence of substructures. A complex lens galaxy mass distribution can dominate flux ratio anomalous phenomenon in the system. Although the number of radio loud flux anomalous lensed quasars remains small, new technique using narrow-line emission will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. One must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis. For the case oringinated by real substructures, mass distribution of lens galaxy may also influence the estimated mass and other derived properties. We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar. For precise estimation on substurcture population, mass function, or any derived properties from strong lensed flux anomalous quasars, non-substructure effects are important to be understood beforehand.

Our result also shows that multi-wavelength image is helpful on exploring flux anomalous lensed quasars. While radio band provides reliable data on positions and fluxes of lensed images, optical and near-infrared imaging provides more information on mass distribution of the lens galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging can help to improve lens modelling. The improvement is even more dramatic in B1555+375. With an high ellipcity edge-on disk, our new lens models well explain the flux ratio anomalies. Lack of knowledge on lens galaxy can lead to an improper lens model and thus cause bias to statics and derived properties among substructure detection. With the first system being analyzed and shown that an edge-on disk from lens galaxy can dominate its flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
